% !TeX root = ../SDonchezThesis.tex

\pagestyle{empty}
\chapter{Acknowledgment}
This work is the culmination of a two year research effort conducted in the course of my Master's studies in the department of Electrical and Computer Engineering at Villanova University. In that time, I have had the privilege of interacting with many incredibly knowledgeable individuals who have played crucial roles in my education. I would like to thank my advisor, Dr. Xiaofang Wang, for her support throughout this process, as well as for encouraging me to pursue a graduate education during my senior year of undergraduate study. I would also like to thank Dr. Richard Perry and Dr. Sarvesh Kulkarni for their gracious assistance in answering questions that arose during the course of my study, as well as Dr. Hubertus Franke, IBM T.J. Watson Research Center and coauthor of \cite{chen_enabling_2014}, for his guidance and interest when contacted in the course of my research.

I would be remiss to not acknowledge with great gratitude Dr. Kyle Juretus and Dr. Jiafeng Xie, who have agreed to dedicate their time to participate in my thesis defense and review process, as well as Dr. Bijan Mobasserri, ECE department chair for the same. Dr. Mobasserri and Dr. Wang also deserve my extreme gratitude for the Tuition Scholarship that I have been provided with for the duration of my graduate studies, without which I would not be undertaking this effort in the first place.

I would also like to thank Professor Edward Char and the late Dr. Edward Kresch, whose passion and knowledge in the field of computer engineering were so instrumental in shaping my undergraduate experience and developing my passion in this field. Finally, but certainly not least, I would like to thank my family and friends for their encouragement and support throughout this process, and for their nods of faux understanding whenever I started talking to them at length about the intricacies of this field.